\Title

### 2021-01-15 manuscript/manuscript.tex
Incorporate australia figures to manuscript

% Import files with parameter values generated by notebooks
\newcommand{\Gal}{Gal}
\input{synthetic-surveys.tex}
\input{parameters-ground-survey.tex}
\input{parameters-airborne-survey.tex}
\input{best-parameters-ground-survey.tex}
\input{best-parameters-airborne-survey.tex}
\input{source-layouts-schematics.tex}
\input{boost-overlapping.tex}

@@

\begin{figure}
    \includegraphics[width=\linewidth]{figs/australia-data.pdf}
    \caption{
    }
    \label{fig:australia-data}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\linewidth]{figs/australia-disturbance.pdf}
    \caption{
    }
    \label{fig:australia-disturbance}
\end{figure}

We start the interpolation process by defining a set of block-averaged sources
at a relative depth of \AustraliaRelativeDepth{}.
The choice of the block spacing must be done taking into account the desired
resolution of the final grid.
If the grid will have a much higher resolution than the block spacing, the
equivalent sources will not be able to reproduce the high frequency components
of the data.
Therefore we recommend setting a block spacing that matches the resolution of
the final grid.
In this case we will generate a regular grid with a resolution of 1~arc-minute,
which can be approximated by \SI{1.8}{\kilometer} for the Earth.

>>>>

% Import files with parameter values generated by notebooks
\newcommand{\Gal}{Gal}
\input{synthetic-surveys.tex}
\input{parameters-ground-survey.tex}
\input{parameters-airborne-survey.tex}
\input{best-parameters-ground-survey.tex}
\input{best-parameters-airborne-survey.tex}
\input{source-layouts-schematics.tex}
\input{boost-overlapping.tex}
\input{australia.tex}

@@

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/australia-data-gravity.png}
    \caption{
    }
    \label{fig:australia-data-gravity}
\end{figure*}

@@

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/australia-data-disturbance.png}
    \caption{
    }
    \label{fig:australia-data-disturbance}
\end{figure*}

We start the interpolation process by defining a set of block-averaged sources
at a relative depth of \AustraliaEqlDepth{}.
The choice of the block spacing must be done taking into account the desired
resolution of the final grid.
If the grid will have a much higher resolution than the block spacing, the
equivalent sources will not be able to reproduce the high frequency components
of the data.
Therefore we recommend setting a block spacing that matches the resolution of
the final grid.
In this case we will generate a regular grid with a resolution of 1~arc-minute,
which can be approximated by \SI{1.8}{\kilo\meter} for the Earth.

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/australia-grid.png}
    \caption{
    }
    \label{fig:australia-grid}
\end{figure*}
